Enzo: An Adaptive Mesh Refinement Code for Astrophysics

### 2013-05-07 development.tex
More description of the development process.

The main development streams of \enzo\ were eventually merged using
the distributed version control system (DVCS) Mercurial
(\url{http://mercurial.selenic.com/}) into a branch of the code known
as \texttt{week-of-code}, so named after the in-person development
sprint at which it was created.  The fundamental, and transformative,
distinction between the previous \textit{centralized} version control
system and mercurial's \textit{distributed} version control system is
the elimination of gatekeepers.  While there still exists a canonical,
central location where stable and development versions of \enzo\ can
be obtained, changesets and versions can be exchanged between peers
without the intervention of designated gatekeepers.  This has the
direct effect of enabling local development to be versioned and its
provenance ensured, while still retaining the ability to benefit from
``upstream'' development.  An important, even crucial, side effect is
that the technology used for local versioning provides mechanisms for
easily submitting locally-developed modifications to the community
source location.  Mercurial internally represents all changes as nodes
in a directed, acyclic graph (DAG), which results in the natural
ability to more consistently and easily manage merging development
streams.

>>>>

A version developed at Penn State and Stanford forked from a version
prior to the LCA version and was the one in which MHD with Dedener
divergence cleaning, the MUSCL hydro solvers, the ray tracing
radiative transfer module, relativistic fluid dynamics, the shearing
box boundaries and updates to the multi-species chemistry were
included. This version was the one that was eventually merged using
the distributed version control system (DVCS) Mercurial
(\url{http://mercurial.selenic.com/}) into a branch of the code known
as \texttt{week-of-code}, so named after the in-person development
sprint at KIPAC in June 2009 at which it was created.  The
fundamental, and transformative, distinction between the previous
\textit{centralized} version control system and mercurial's
\textit{distributed} version control system is the elimination of
gatekeepers.  While there still exists a canonical, central location
where stable and development versions of \enzo\ can be obtained,
changesets and versions can be exchanged between peers without the
intervention of designated gatekeepers.  This has the direct effect of
enabling local development to be versioned and its provenance ensured,
while still retaining the ability to benefit from ``upstream''
development.  An important, even crucial, side effect is that the
technology used for local versioning provides mechanisms for easily
submitting locally-developed modifications to the community source
location.  Mercurial internally represents all changes as nodes in a
directed, acyclic graph (DAG), which results in the natural ability to
more consistently and easily manage merging development streams.
